---
  title: "testing R Markdown bis bis"
  author: "Marco Baldo"
  output: 
   pdf_document: default
  date: 2023/06/14
---

# Say Hello to markdown


Markdown is an **easy to use** format for writing reports. It resembles what you naturally write every time you compose an email. In fact, you may have already used markdown *without realizing it*. These websites all rely on markdown formatting.
In case word is not working use *tinytex::install_tinytex()* before to start.

* [Github](www.github.com)
* [StackOverflow](www.stackoverflow.com)
* [Reddit](www.reddit.com)

eval = TRUE evaluate the script

echo = FALSE means only the result shown

message = FALSE remove the messages from the report

warnings = FALSE remove the warning messages

Here’s some code

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(eval=FALSE, echo = TRUE, message = FALSE, warning = FALSE)

library(ggplot2)
library(raster)
library(fields)
library(tidyr)
library(cowplot)
library(dplyr)
library(purrr)

getwd()
```

```{r, eval = TRUE}
a <- 5
b <- 3
c <- a+b

c
```


```{r, eval = FALSE}
a <- 5
b <- 3
c <- a+b

c
```

```{r, echo = FALSE}
a <- 5
b <- 3
c <- a+b

c
```

```{r, eval = TRUE, echo = TRUE, message=FALSE, warning=FALSE}
library(ggplot2)

getwd()

file<-"../../../AAAAA/bily_kriz_3km_n.annout" # ../../ is the code for search 
                     # the file one or two or more step of the computer path
a<-read.table(file,header=T)
print(a)

plot(a$year,a$totalc)

ggplot(a, aes(year, totalc))+
       geom_line(size=1.2, show.legend = F)

```